EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems

### 2025-05-07 05_examples.tex
Few typos
GB: heavy rewrite of the iRDM (3.10) section
Summation indices were misleading, the normal case was written (in the formula) to be diagonal, which is not for Norb > 1. The listing were correct, so it was just a matter of notational mess. I also added a formal proof to why the normal iRDM is block-diagonal with respect to impurity Nup and Ndw sectors.
It should read pretty smooth now.

I also edited many sub- and super-scripts, adding the usual \mathrm{}, when they are words (bath, imp, int, e-ph, ...)

Finally, I did some light editing on the Attractive Hubbard example, just because

The iterative algorithm proceeds as follows:
\begin{enumerate}
\item Call the exact diagonalization {\bf impurity solver} {\tt
    ed\_solve} whose only input is the set of parameters $\vec{x}$. All other
  options are controlled by input file specifications ({\tt
    ed\_read\_input}).
\item Retrieve at least the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
  Matsubara axis using {\tt ed\_get\_sigma}.
\item Evaluate the local interacting Green's function
  $G_{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
  \item Update the Weiss field through the {\bf self-consistency}
    relation: $\GG^{-1}_0(i\omega) = G_{loc}(i\omega) + \Sigma(i\omega)$. 
  \item Optimize the bath parameters $\vec{x}$ against the updated
    Weiss field using, for instance, {\tt ed\_chi2\_fitgf}. Restart at 1.
\end{enumerate}
In agreement with Reverse Communication Strategy setup, the step 3-4
are left to the user. In addition step 5 is kept separated to
guarantee enough freedom in the bath optimization, though we remark
this is a crucial step which can potentially compromise the whole
calculation.
An example of implementation is given in the following listings.

@@

To illustrate this point, we report in panel (A) the evolution of
the spectral function $-{\rm Im}G_{loc}(\omega)/\pi$ as a function of
the interaction strenght $U$. Despite the {\it spiky} nature of the spectrum, due to the
finite size (i.e. number of poles) of the discretized effective bath,
it is possible to clearly distinguish the characteristic features of
the Mott transition. At low energy, we observe the renormalization of the 
quasi-particle peak at the Fermi level ($\omega=0$). Concomitantly the
system shows the formation of incoherent  high-energy features which
will then develop into Hubbard bands in the Mott insulating state for $U>U_c$, with $U_c\simeq 2.8D$.

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{figures/figBethe.pdf}
    \caption{\label{figEx1}%
      \textbf{The Metal-Insulator Mott transition.}
      (a) Evolution of the spectral function $-\Im{G}(\omega)/\pi$ as
      a function of increasing interaction $U$. The critical
      interaction $U_c\simeq 2.8D$ separates the correlated metal $U<U_c$ from
      the Mott insulator $U>U_c$.
      (b)-(c) The corresponding evolution of the Matsubara self-energy
      $\Im\Sigma(i\omega)$ (b) and
      real-axis one $\Re\Sigma(\omega)$ across the Mott
      transition. For a particle-hole symmetric case both allow to
      estimate the renormalization constant $Z$ (see main text), using
      linear order expansion in frequency (blue solid lines). The
      values of $Z$ are reported in the legend.
      The Mott insulating solution is associated to a singularity at
      $\omega=0$ of $\Im\Sigma$. 
        }
\end{figure}

The formation of a spectral gap separating the Hubbard bands in the
Mott insulator is supported by the divergence, at the Fermi level, of the imaginary part of
the self-energy function. Causality imposes that the real-part of
this quantity becomes large near the singularity making it impossible
to satisfy the quasi-particles poles equations
$\omega+\mu-h^0-\e-\Re{\Sigma}(\omega)=0$, i.e. preventing coherent
quasi-particles excitations near the Fermi level. 
In the panels (B) and (C) we discuss this point  showing the evolution
of the self-energy functions $\Sigma$.
Specifically, in panel (B) we report the self-energy ${\rm Im}\Sigma(i\omega)$
on the Matsubara axis in the low energy regime. Increasing $U$
we observe the progressive growth of this function until a
diverging behavior is acheived crossing the critical interaction
strenght $U>U_c$.
We recall that this behavior can be observed on the Matsubara axis
because of the particle-hole symmetry of the problem which pins the
$\Im{\Sigma}$ singularity at $\omega=0$.
In panel (C), we report the corresponding behavior of the
$\Re{\Sigma}(\omega)$ in small energy regime around the Fermi
level. Augmenting the interaction strength $U$ leads to a sudden
increase of this self-energy component until a discontinuous behavior
is reached, associated to the divergence of the corresponding
imaginary part.

@@

The DMFT workflow for this case is very similar to the previous one
provided works in the Nambu basis defined by the spinor
$\psi_i=[c_{i\up}, c^+_{i\dw}]^t$.
In this basis any correlation functions, e.g. the Green's function, takes the matrix form:
\begin{equation}
  {\mathbf G} =
  \begin{pmatrix}
    \hat{G}_{\uparrow\uparrow} & \hat{F}_{\uparrow\downarrow}\\
    \hat{\bar{F}}_{\downarrow\uparrow}  &    \hat{\bar{G}}_{\downarrow\downarrow} \\
   \end{pmatrix}
\end{equation}
where the symbol $\hat{A}$ indicates the possible multi-orbital
character which reduced to a scalar in the present case of a single
orbital. The symbol $\hat{\bar{A}}$ indicates that the components in
the second row are connect by particle-hole and time-reversal
symmetries to the first row one. The specific relation depends on the
symmetry of the order parameter (here $s$-wave) and the nature of the
complex argument of the functions, i.e. Matsubara or real-axis:
\begin{equation}
\begin{array}{cc}
  \hat{\bar{G}}(i\omega) = -\hat{G}^*(i\omega)\;; &  \hat{\bar{F}}(i\omega) = \hat{F}(i\omega)\\
  \hat{\bar{G}}(\omega)  = -\hat{G}^*(-\omega) \;; & \hat{\bar{F}}(\omega) = \hat{F}^*(i\omega)\\
\end{array}
\end{equation}  
The code implementation closely follows the previous structure, with
some notable exceptions related to the Nambu structure for which,
using the symmetries above, we only need to deal with the first row
independent components. In the first part of the code we initialize
the lattice structure and the solver:
\begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
import numpy as np
from edipy2 import global_env as ed
import mpi4py
from mpi4py import MPI
import os,sys
from aux_funx import * #include function to build $G_{loc}$ and Weiss fields

@@

The iterative scheme for the solution of DMFT closely follows the
sequence discussed in \secu{SecExamplesBetheDMFT}:   
\begin{enumerate}
\item Call the exact diagonalization {\bf impurity solver} {\tt
    ed.solve} providing the set of bath parameters $\vec{x}=\{V,h\}$  as input. 
\item Using the dedicated
  input/output procedures {\tt ed.get\_sigma} we retrieve the self-energy functions  
  $\hat{\Sigma}(i\omega)$ and $\hat{S}(i\omega)$ on the 
  Matsubara axis.
\item
  Evaluate the interacting local Green's functions $\hat{G}_{loc}$ and
  $\hat{F}_{loc}$:
  \begin{equation}
  {\mathbf G}_{loc}(i\omega) =
  \int_\RRR d\e \rho(\e)
  \begin{pmatrix}
    (i\omega +\mu)\hat{\11} - \hat{h}^0 - \hat{\Sigma}(i\omega) -\e & -\hat{S}(i\omega) \\
    -\hat{S}(i\omega) & (i\omega +\mu)\hat{\11} + \hat{h}^0 +
    \hat{\Sigma}^*(i\omega) +\e\\
  \end{pmatrix}^{-1}
\end{equation}
\item Update the normal and anomalous Weiss fields, respectively 
  $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
    relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}_{loc}(i\omega) +
    {\mathbf \Sigma}(i\omega)$ in Nambu space. 
  \item Optimize the bath parameters $\vec{x}$ to best describe the  updated
    Weiss fields using \NAME provided conjugate gradient  fit
    procedure {\tt ed.chi2\_fitgf}.
\end{enumerate}
which is implemented in Python as follows:
\begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
#DMFT CYCLE
converged=False;iloop=0
while (not converged and iloop<ed.Nloop ):
iloop=iloop+1

@@

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{figures/figAHM.pdf}
    \caption{\label{figEx2}%
      \textbf{The BCS to BEC crossover.}
      (a) Evolution of the spectral functions
      $-\Im{G_{loc}(\omega)}/\pi$ as a function of increasing
      attraction $U$. 
      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
      function of the attraction $U$. Data for BCS (gray) is compared
      to DMFT results (blue line and symbols). 
      (c) The correlation strength
      $\Theta=\frac{|S(i\omega\to0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$ as a function of the
      attraction $U$ across the BCS-BEC crossover. 
      (d) Comparison of the double occupation $D=\langle n_\up
      n_\dw\rangle$ as a function of attraction $U$ between BCS (gray
      solid line) and DMFT (blue solid line and symbols). 
      (e) Superconducting order
      parameter $\phi$ as a function of temperature across the
      superconductor-to-normal phase transition. Data for $U=4$. The
      fit highlights the critical behavior with a mean-field exponent
      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_c=0.61$.       
        }
\end{figure}

@@

To beging with, we report in  panel (A) of \figu{figEx2} the
evolution of the spectral density, obtained from the local normal
Green's function $-\tfrac{1}{\pi}\Im{G}_{loc}(\omega)$, as a function
of the attraction $U$. For any finite value of  $U$ the Van Hove peak
at $\omega=0$ of the 2D square lattice (see $U=0$
solution) gets split by the formation of a superconductive gap of
width which increases with $U$.
The existence of a gap is associated to the formation of a finite
order parameter $\phi=\langle c_\up c_\dw\rangle$. The behavior of
this quantity, shown in panel (B), highlights crossover from the BCS
regime at weak coupling to a BEC one for large $U$.
The former regime is characterized by the well known exponential increase of
$\phi$, which is computationally the hardest regime to adress. At
strong coupling or BEC regime the order parameter saturates to its
limiting value $\phi\to 1/2$. The comparison with mean-field result
(gray) underlines the effect of local quantum fluctuations in slightly
suppressing the order parameter. This effect is particularly active in
the intermediate regime, as captured by the behavior of the
correlation strength
$\theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
reported in panel (C). Assuming a monotonic behavior of the anomalous
self-energy function, this quantity estimates the ``strength'' of
quantum fluctuations comparing the mean-field-like behavior at high
energy scale with that near the Fermi level. A large value of $\theta$
indicates a more correlated system.
Our results show that both weak and strong coupling regime are
relatively weakly correlated, i.e. very near a mean-field solution. On
the contrary, the inter-mediate regime is characterized by a large
correlation, making the solution very different from that obtained in
BCS description.  
To further corroborate the distance between the DMFT and mean-field
solution we report in panel (D) the evolution of the double occupancy
$d=\langle n_\up n_\dw\rangle$. At half-filling the mean-field value is
determined solely by the order parameter as $d=1/4 + \phi^2$.
Our results show that the inclusion of quantum fluctuations in DMFT
slightly increase the value of $d$ in the weak coupling
regime. However, increasing the attraction the double occupations
quickly get reduced below the mean-field value up to the BEC regime.

Finally, we illustrate the capability of \NAME in
exploring finite temperature physics. In panel (E) we show the
temperature evolution of the order parameter $\phi(T)$ across the
superconductor-to-normal transition. The mean-field nature of this
transition is underlined by the scaling of  the solution near
the critical point $\phi \simeq (T_c-T)^\beta$ with $\beta=1/2$ as
predicted by mean-field calculations.

\subsection{Multi-orbital Hubbard (Triqs)}

>>>>

The iterative algorithm proceeds as follows:
\begin{enumerate}
\item Call the exact diagonalization {\bf impurity solver} {\tt
    ed\_solve} whose only input is the set of parameters $\vec{x}$. All other
  options are controlled by input file specifications ({\tt
    ed\_read\_input}).
\item Retrieve at least the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
  Matsubara axis using {\tt ed\_get\_sigma}.
\item Evaluate the local interacting Green's function
  $G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
  \item Update the Weiss field through the {\bf self-consistency}
    relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) + \Sigma(i\omega)$. 
  \item Optimize the bath parameters $\vec{x}$ against the updated
    Weiss field using, for instance, {\tt ed\_chi2\_fitgf}. Restart at 1.
\end{enumerate}
In agreement with Reverse Communication Strategy setup, the step 3-4
are left to the user. In addition step 5 is kept separated to
guarantee enough freedom in the bath optimization, though we remark
this is a crucial step which can potentially compromise the whole
calculation.
An example of implementation is given in the following listings.

@@

To illustrate this point, we report in panel (A) the evolution of
the spectral function $-{\rm Im}G_\mathrm{loc}(\omega)/\pi$ as a function of
the interaction strenght $U$. Despite the {\it spiky} nature of the spectrum, due to the
finite size (i.e. number of poles) of the discretized effective bath,
it is possible to clearly distinguish the characteristic features of
the Mott transition. At low energy, we observe the renormalization of the 
quasi-particle peak at the Fermi level ($\omega=0$). Concomitantly the
system shows the formation of incoherent  high-energy features which
will then develop into Hubbard bands in the Mott insulating state for $U>U_\mathrm{c}$, with $U_\mathrm{c}\simeq 2.8D$.

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{figures/figBethe.pdf}
    \caption{\label{figEx1}%
      \textbf{The Metal-Insulator Mott transition.}
      (a) Evolution of the spectral function $-\Im{G}(\omega)/\pi$ as
      a function of increasing interaction $U$. The critical
      interaction $U_\mathrm{c}\simeq 2.8D$ separates the correlated metal $U<U_\mathrm{c}$ from
      the Mott insulator $U>U_\mathrm{c}$.
      (b)-(c) The corresponding evolution of the Matsubara self-energy
      $\Im\Sigma(i\omega)$ (b) and
      real-axis one $\Re\Sigma(\omega)$ across the Mott
      transition. For a particle-hole symmetric case both allow to
      estimate the renormalization constant $Z$ (see main text), using
      linear order expansion in frequency (blue solid lines). The
      values of $Z$ are reported in the legend.
      The Mott insulating solution is associated to a singularity at
      $\omega=0$ of $\Im\Sigma$. 
        }
\end{figure}

The formation of a spectral gap separating the Hubbard bands in the
Mott insulator is supported by the divergence, at the Fermi level, of the imaginary part of
the self-energy function. Causality imposes that the real-part of
this quantity becomes large near the singularity making it impossible
to satisfy the quasi-particles poles equations
$\omega+\mu-h^0-\e-\Re{\Sigma}(\omega)=0$, i.e. preventing coherent
quasi-particles excitations near the Fermi level. 
In the panels (B) and (C) we discuss this point  showing the evolution
of the self-energy functions $\Sigma$.
Specifically, in panel (B) we report the self-energy ${\rm Im}\Sigma(i\omega)$
on the Matsubara axis in the low energy regime. Increasing $U$
we observe the progressive growth of this function until a
diverging behavior is acheived crossing the critical interaction
strenght $U>U_\mathrm{c}$.
We recall that this behavior can be observed on the Matsubara axis
because of the particle-hole symmetry of the problem which pins the
$\Im{\Sigma}$ singularity at $\omega=0$.
In panel (C), we report the corresponding behavior of the
$\Re{\Sigma}(\omega)$ in small energy regime around the Fermi
level. Augmenting the interaction strength $U$ leads to a sudden
increase of this self-energy component until a discontinuous behavior
is reached, associated to the divergence of the corresponding
imaginary part.

@@

The DMFT workflow for this case is very similar to the previous one
provided works in the Nambu basis defined by the spinor
$\psi_i=[c_{i\up}, c^+_{i\dw}]^t$.
In this basis any correlation functions, e.g. the Green's function, takes the matrix form:
\begin{equation}
  {\mathbf G} =
  \begin{pmatrix}
    \hat{G}_{\uparrow\uparrow} & \hat{F}_{\uparrow\downarrow}\\
    \hat{\bar{F}}_{\downarrow\uparrow}  &    \hat{\bar{G}}_{\downarrow\downarrow} \\
   \end{pmatrix}
\end{equation}
where the symbol $\hat{A}$ indicates the possible multi-orbital
character which reduced to a scalar in the present case of a single
orbital. The symbol $\hat{\bar{A}}$ indicates that the components in
the second row are connect by particle-hole and time-reversal
symmetries to the first row one. The specific relation depends on the
symmetry of the order parameter (here $s$-wave) and the nature of the
complex argument of the functions, i.e. Matsubara or real-axis:
\begin{equation}
\begin{array}{cc}
  \hat{\bar{G}}(i\omega) = -\hat{G}^*(i\omega)\;; &  \hat{\bar{F}}(i\omega) = \hat{F}(i\omega)\\
  \hat{\bar{G}}(\omega)  = -\hat{G}^*(-\omega) \;; & \hat{\bar{F}}(\omega) = \hat{F}^*(i\omega)\\
\end{array}
\end{equation}  
The code implementation closely follows the previous structure, with
some notable exceptions related to the Nambu structure for which,
using the symmetries above, we only need to deal with the first row
independent components. In the first part of the code we initialize
the lattice structure and the solver:
\begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
import numpy as np
from edipy2 import global_env as ed
import mpi4py
from mpi4py import MPI
import os,sys
from aux_funx import * #include function to build $G_\mathrm{loc}$ and Weiss fields

@@

The iterative scheme for the solution of DMFT closely follows the
sequence discussed in \secu{SecExamplesBetheDMFT}:   
\begin{enumerate}
\item Call the exact diagonalization {\bf impurity solver} {\tt
    ed.solve} providing the set of bath parameters $\vec{x}=\{V,h\}$  as input. 
\item Using the dedicated
  input/output procedures {\tt ed.get\_sigma} we retrieve the self-energy functions  
  $\hat{\Sigma}(i\omega)$ and $\hat{S}(i\omega)$ on the 
  Matsubara axis.
\item
  Evaluate the interacting local Green's functions $\hat{G}_\mathrm{loc}$ and
  $\hat{F}_\mathrm{loc}$:
  \begin{equation}
  {\mathbf G}_\mathrm{loc}(i\omega) =
  \int_\RRR d\e \rho(\e)
  \begin{pmatrix}
    (i\omega +\mu)\hat{\11} - \hat{h}^0 - \hat{\Sigma}(i\omega) -\e & -\hat{S}(i\omega) \\
    -\hat{S}(i\omega) & (i\omega +\mu)\hat{\11} + \hat{h}^0 +
    \hat{\Sigma}^*(i\omega) +\e\\
  \end{pmatrix}^{-1}
\end{equation}
\item Update the normal and anomalous Weiss fields, respectively 
  $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
    relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}_\mathrm{loc}(i\omega) +
    {\mathbf \Sigma}(i\omega)$ in Nambu space. 
  \item Optimize the bath parameters $\vec{x}$ to best describe the  updated
    Weiss fields using \NAME provided conjugate gradient  fit
    procedure {\tt ed.chi2\_fitgf}.
\end{enumerate}
which is implemented in Python as follows:
\begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
#DMFT CYCLE
converged=False;iloop=0
while (not converged and iloop<ed.Nloop ):
iloop=iloop+1

@@

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{figures/figAHM.pdf}
    \caption{\label{figEx2}%
      \textbf{The BCS to BEC crossover.}
      (a) Evolution of the spectral functions
      $-\Im{G_\mathrm{loc}(\omega)}/\pi$ as a function of increasing
      attraction $U$. 
      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
      function of the attraction $U$. Data for BCS (gray) is compared
      to DMFT results (blue line and symbols). 
      (c) The correlation strength
      $\Theta=\frac{|S(i\omega\to0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$ as a function of the
      attraction $U$ across the BCS-BEC crossover. 
      (d) Comparison of the double occupation $D=\langle n_\up
      n_\dw\rangle$ as a function of attraction $U$ between BCS (gray
      solid line) and DMFT (blue solid line and symbols). 
      (e) Superconducting order
      parameter $\phi$ as a function of temperature across the
      superconductor-to-normal phase transition. Data for $U=4$. The
      fit highlights the critical behavior with a mean-field exponent
      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_\mathrm{c}=0.61$.       
        }
\end{figure}

@@

To beging with, we report in  panel (A) of \figu{figEx2} the
evolution of the spectral density, obtained from the local normal
Green's function $-\tfrac{1}{\pi}\Im{G}_\mathrm{loc}(\omega)$, as a function
of the attraction $U$. For any finite value of  $U$ the Van Hove peak
at $\omega=0$ of the 2D square lattice (see $U=0$
solution) gets split by the formation of a superconductive gap of
width which increases with $U$.
The existence of a gap is associated to the formation of a finite
order parameter $\phi=\langle c_\up c_\dw\rangle$. The behavior of
this quantity, shown in panel (B), highlights crossover from the BCS
regime at weak coupling to a BEC one for large $U$.
The former regime is characterized by the well known exponential increase of
$\phi$, which is computationally the hardest regime to adress. At
strong coupling or BEC regime the order parameter saturates to its
limiting value $\phi\to 1/2$. The comparison with mean-field result
(gray) underlines the effect of local quantum fluctuations in slightly
suppressing the order parameter. This effect is particularly active in
the intermediate regime, as captured by the behavior of the so-called
\emph{correlation strength}
$\Theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
reported in panel (C). Assuming a monotonic behavior of the anomalous
self-energy function, this quantity estimates the ``strength'' of its
dynamical fluctuations, comparing the mean-field-like behavior found
at high energy scale, with the features at the Fermi level. 
A large value of $\Theta$ indicates a more dynamical self-energy, hence
a more correlated system.
Our results show that both weak and strong coupling regime are
relatively weakly correlated, i.e. very near a mean-field solution. On
the contrary, the inter-mediate regime is characterized by a large
correlation, making the solution very different from that obtained in
BCS description.  
To further corroborate the distance between the DMFT and the mean-field
solutions, we report in panel (D) the evolution of the double occupancy
$d=\langle n_\up n_\dw\rangle$. At half-filling the mean-field value is
determined solely by the order parameter as $d=1/4 + \phi^2$.
Our results show that the inclusion of dynamical fluctuations in DMFT
slightly increase the value of $d$ in the weak coupling
regime. However, increasing the attraction the double occupations
quickly get reduced below the mean-field value up to the BEC regime.

Finally, we illustrate the capability of \NAME in
exploring finite temperature physics. In panel (E) we show the
temperature evolution of the order parameter $\phi(T)$ across the
superconductor-to-normal transition. The mean-field nature of this
transition is underlined by the scaling of the solution near
the critical point $\phi \simeq (T_\mathrm{c}-T)^\beta$ with $\beta=1/2$ as
predicted by mean-field calculations.

\subsection{Multi-orbital Hubbard (TRIQS)}
